---
title: "CDM Data Quality Report"
subtitle: "Summary report"
author: ""
institute: ""
date: ""
output: 
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '5'
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

---

### Important Notes


You can write here any important issues you have encountered when reviewing the data.

---

```{r library, include=FALSE}
library(dplyr)
library(readr)
library(purrr)
library(ggplot2)
library(tidyr)
library(knitr)
library(DT)
```


### Data release

```{r include=FALSE}
# Compare previous database version with new one
database1 = "omop_old1"
database2 = "omop_new1"

#Default values
runCheckDB1 = FALSE
runCheckDB2 = FALSE

## Database 1 ------------------------------------------------------------------
path1 = file.path(here::here(), database1)
if(dir.exists(path1)){
  csv_files1 <- list.files(path = path1, pattern = "\\.csv", full.names = TRUE)
} 
#Generate results
if(!dir.exists(path1)){
  runCheckDB1 = TRUE
} else if(is_empty(csv_files1)){
  runCheckDB1 = TRUE
}

## Database 2 ------------------------------------------------------------------
path2 = file.path(here::here(), database2)
if(dir.exists(path2)){
  csv_files2 <- list.files(path = path2, pattern = "\\.csv", full.names = TRUE)
}
#Generate results
if(!dir.exists(path2)){
  runCheckDB2 = TRUE
} else if(is_empty(csv_files2)){
  runCheckDB2 = TRUE
}

```



```{r, include=FALSE}
# Run result generation if did not found csv files
mother_table_name <- "pregnancy_episode" #set to NULL if does not exist
minimum_counts <- 5

driver = RPostgres::Postgres()   #change it based on DBMS

if(any(c(runCheckDB1, runCheckDB2))){

  # load functions
  source(here::here("functions.R"))

  if(runCheckDB1){
    # Get results previous database instance
    getChecksData(dbms = driver, 
                  server_dbi = Sys.getenv("DB_SERVER"),
                  port = Sys.getenv("DB_PORT"),
                  host = Sys.getenv("DB_HOST"),
                  user = Sys.getenv("DB_USER"),
                  password = Sys.getenv("DB_PASSWORD"),
                  cdm_schema = "...",
                  write_schema = "...",
                  output_folder = path1)
  }
  if(runCheckDB2){
    # Get results new database instance
    getChecksData(dbms = driver, 
                  server_dbi = Sys.getenv("DB_SERVER_NEW"),
                  port = Sys.getenv("DB_PORT_NEW"),
                  host = Sys.getenv("DB_HOST_NEW"),
                  user = Sys.getenv("DB_USER_NEW"),
                  password = Sys.getenv("DB_PASSWORD_NEW"),
                  cdm_schema = "...",
                  write_schema = "...",
                  output_folder = path2)
  }
}
```


```{r, include=FALSE}
#Load results already generated
data1 <- list()
for (file in csv_files1) {
  table_name <- tools::file_path_sans_ext(basename(file))
  df <- read_csv(file)%>%
    mutate(db=database1)
  data1[[table_name]] <- df
}
#Load results already generated
data2 <- list()
for (file in csv_files2) {
  table_name2 <- tools::file_path_sans_ext(basename(file))
  df2 <- read_csv(file)%>%
    mutate(db=database2)
  data2[[table_name2]] <- df2
}

```

```{r data_release, echo=FALSE}
if ("cdm_snapshot" %in% names(data1)) {
  df=data1$cdm_snapshot %>%
    mutate(cdm_inst=database1)%>%
    add_row(data2$cdm_snapshot%>%
    mutate(cdm_inst=database2))%>%
    select(cdm=cdm_name,inst=cdm_inst, version=cdm_version, release_date=cdm_release_date,
           voc_version=vocabulary_version, person_count, lastest_obs = 
             latest_observation_period_end_date, snapshot=snapshot_date)
  kable(df)
}
```


### Birth and death dates

```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("birth" %in% names(data1)) {
  data1$birth%>%
    add_row(data2$birth)%>%
    ggplot(aes(x=year_of_birth, y=n, color=db, fill=db))+
    facet_grid(db ~ sex)+
    geom_bar(stat="identity")+
    labs(subtitle = "Number of births over time, stratified by sex")
}
```


```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("death" %in% names(data1)) {
  data1$death %>%
    add_row(data2$death)%>%
    ggplot(aes(x=death_date, y=n,color=db, fill=db))+
    geom_bar(stat="identity", position=position_dodge())+
    labs(subtitle = "Number of deaths per year")
}
```

### Observation periods
```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("observation_period" %in% names(data1)) {
  data1$observation_period%>%
    gather("obs_date", "n", c(-1,-4))%>%
    add_row(data2$observation_period%>%
    gather("obs_date", "n", c(-1,-4)))%>%
    mutate(date=as.Date(date))%>%
    mutate(obs_date = factor(obs_date, levels = c("n_start","n_end")))%>%
    ggplot(aes(x=date, y=n, color=obs_date, fill=obs_date))+
    geom_bar(stat="identity", position = position_dodge())+
    facet_grid(db ~ .)+
    scale_x_date(date_breaks="2 year", date_labels="%Y")+
    scale_fill_manual(values = c("n_start" = "#1b9e77", "n_end" = "#d97f02")) +
    scale_color_manual(values = c("n_start" = "#1b9e77", "n_end" = "#d97f02"))+
    labs(subtitle = "Observation dates")
}
```



```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("observation_period" %in% names(data1)) {
  data1$observation_period%>%
    gather("obs_date", "n", c(-1,-4))%>%
    add_row(data2$observation_period%>%
    gather("obs_date", "n", c(-1,-4)))%>%
    mutate(date=as.Date(date))%>%
    mutate(obs_date = factor(obs_date, levels = c("n_start","n_end")))%>%
    group_by(db)%>%
    arrange(date)%>%
    slice(-1)%>%
    slice(1:(n()-1))%>%
    ggplot(aes(x=date, y=n, color=obs_date, fill=obs_date))+
    geom_bar(stat="identity", position = position_dodge())+
    facet_grid(db ~ .)+
    scale_x_date(date_breaks="2 year", date_labels="%Y")+
    scale_fill_manual(values = c("n_start" = "#1b9e77", "n_end" = "#d97f02")) +
    scale_color_manual(values = c("n_start" = "#1b9e77", "n_end" = "#d97f02"))+
    labs(subtitle = "Observation dates excluding database start and end dates")
}

```

### Pregnancies
```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("pregnancies" %in% names(data1)) {
  data1$pregnancies%>%
    gather("pregnancy_date", "n", c(-1,-4))%>%
    add_row(data2$pregnancies %>%
    gather("pregnancy_date", "n", c(-1,-4)))%>%
    mutate(date=as.Date(date))%>%
    mutate(pregnancy_date = factor(pregnancy_date, levels = c("n_start","n_end")))%>%
    ggplot(aes(x=date, y=n, color=pregnancy_date, fill=pregnancy_date))+
    geom_bar(stat="identity", position = position_dodge())+
    facet_grid(db ~ .)+
    scale_x_date(date_breaks="2 year", date_labels="%Y")+
    scale_fill_manual(values = c("n_start" = "#1b9e77", "n_end" = "#d97f02")) +
    scale_color_manual(values = c("n_start" = "#1b9e77", "n_end" = "#d97f02"))
}
```


### Fact relationship

```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("fact_relationship" %in% names(data1)) {
  data1$fact_relationship%>%
    add_row(data2$fact_relationship)%>%
    group_by(db, concept_name) %>% 
    ggplot(aes(x=concept_name, y=n, color=db, fill=db))+
    geom_bar(stat="identity", position = position_dodge(width = 0.5), width = 0.5)+
    geom_text(aes(label = n, group=db), position = position_dodge(width = 0.5), vjust = -0.2, size = 3)
}

```


### CDM tables


```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("table_counts" %in% names(data1)) {
  
  data1$table_counts%>%
    add_row(data2$table_counts)%>%
    group_by(db, table) %>% 
    ggplot(aes(x=table, y=n_rec, color=table, fill=table))+
    geom_bar(
      aes(group = db),                
      stat = "identity",
      position = position_dodge(width = 0.7),
      width = 0.6
    ) +
    geom_text(
      aes(label = db, group = db),
      position = position_dodge(width = 0.8),
      vjust = -0.3,
      size = 2.5
    ) +
    labs(subtitle  ="Number of records")+
    theme(
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
      strip.text = element_text(face = "bold")
    )
}

```

```{r,  fig.width=8, fig.height=5, echo=FALSE}

if ("table_counts" %in% names(data1)) {
  data1$table_counts%>%
    add_row(data2$table_counts)%>%
    group_by(db, table) %>% 
    ggplot(aes(x=table, y=n_sub, color=table, fill=table))+
    geom_bar(
      aes(group = db),                # agrupa por base de datos
      stat = "identity",
      position = position_dodge(width = 0.7),
      width = 0.6
    ) +
    geom_text(
      aes(label = db, group = db),
      position = position_dodge(width = 0.8),
      vjust = -0.3,
      size = 2.5
    ) +
    labs(subtitle  ="Number of subjects")+
    theme(
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
      strip.text = element_text(face = "bold")
    )
}

```



### Visits
```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("visits" %in% names(data1)) {
  data1$visits%>%
    add_row(data2$visits)%>%
    group_by(db, type_visit) %>% 
    summarise(mean_visits_per_year = as.integer(mean(n)), .groups = "keep") %>% 
    ggplot(aes(x=type_visit, y=mean_visits_per_year, color=db, fill=db))+
    geom_bar(
      aes(group = db), 
      stat="identity", 
      position = position_dodge(width = 0.8),
      width = 0.7
    )+
    geom_text(
      aes(label = mean_visits_per_year, group = db),
      position = position_dodge(width = 0.8),
      vjust = -0.3,
      size = 2.5
    ) +
    labs((subtitle  ="Mean number of different type of visits in one year"))
  
  # data1$visits%>%
  #   add_row(data2$visits)%>%
  #   group_by(db, type_visit) %>%   
  #   ggplot(aes(x = date_visit, y = n, color = type_visit)) +  
  #   geom_line(size = 1.2) +
  #   geom_point(size = 2) +
  #   facet_grid(db ~ .) +
  #   labs(
  #     x = "Year",
  #     y = "Mean visits per person",
  #     title = "Trend in Average Visits per Year"
  #   ) +
  #   theme_minimal()
}

```


# Visits per year for the new instance 

```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("visits" %in% names(data2)) {
  data2$visits %>%
    ggplot(aes(x = factor(date_visit), y = n, color = type_visit, fill = type_visit)) +
    geom_bar(stat = "identity", position = position_dodge(width = 0.4), width = 0.6) +
    theme_minimal()+
    theme(
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
      strip.text = element_text(face = "bold")
    )+
    facet_wrap(~ type_visit, ncol = 2, scales = "free_y") +
    labs(subtitle  ="Number of visits per year for the new instance")
}

```


### Procedures
```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("procedures" %in% names(data1)) {
  data1$procedures %>%
    add_row(data2$procedures) %>%
    ggplot(aes(x=vocabulary_id, y=n_total_voc, color=vocabulary_id, fill=vocabulary_id))+
    geom_bar(stat="identity")+
    geom_text(aes(label = n_total_voc), vjust = -0.1, size = 3)+
    facet_grid(db ~ .)+
    labs(subtitle  ="Records of procedures grouped by vocabulary id")
}
```


### Measurements

#### Concepts

Measurement concepts that have changed (removed / added) or have decreased the records/subjects in the new instance

```{r,  fig.width=10, fig.height=4, echo=FALSE}
if ("measurements_concepts" %in% names(data1)) {
  data_mes <- data1$measurements_concepts %>%
    rename(n_rec_old = n_rec, n_sub_old=n_sub, concept_name_old = concept_name) %>% 
    select(-db) %>% 
    full_join(
      data2$measurements_concepts %>% 
        rename(n_rec_new = n_rec, n_sub_new=n_sub, concept_name_new = concept_name) %>% 
        select( -db), 
      by =c("measurement_concept_id")
    ) %>% 
    mutate(n_rec_dif = n_rec_new - n_rec_old, n_sub_dif = n_sub_new - n_sub_old ) 
  
  data_mes %>%
    filter(is.na(n_rec_new)) %>% 
    select(measurement_concept_id, concept_name = concept_name_old, n_rec_old, n_sub_old, n_rec_new, n_sub_new) %>% 
    add_row(data_mes %>%
              filter(is.na(n_rec_old)) %>% 
              select(measurement_concept_id, concept_name = concept_name_new, n_rec_old, n_sub_old, n_rec_new, n_sub_new)
            ) %>% 
    add_row(data_mes %>%
              filter(n_rec_dif < 0 | n_sub_dif <0) %>% 
              select(measurement_concept_id, concept_name = concept_name_new, n_rec_old, n_sub_old, n_rec_new, n_sub_new)
            ) %>% 
    rename(meas_concept_id = measurement_concept_id) %>% 
    mutate(issue = ifelse(is.na(n_rec_new), "removed", ifelse(is.na(n_rec_old), "added", "decreased n"))) %>% 
    datatable(
      filter= "top",
      options = list(
              scrollX = TRUE,     
              scrollY = "400px",  
              pageLength = 100,   
              dom = 't'           
            ))%>%
    formatStyle(
      'issue',
      target = 'row',
      backgroundColor = styleEqual(
        c("removed", "added", "decreased n"), 
        c("lightpink",  "lightgreen", "orange")
      )
    )
    
}


```



### Observation 

#### Source concepts

Observation concepts that have changed (removed / added) or have decreased the records/subjects in the new instance

```{r,  fig.width=8, fig.height=4, echo=FALSE}
if ("observation_source_values" %in% names(data1)) {
  diff_in_data2 <- data2$observation_source_values %>%
    anti_join(data1$observation_source_values, by = "observation_source_value")
  
  data_obs_all <- diff_in_data2 %>% 
      select(observation_source_value, source_concept_name, obs_concept_id, n_24 =n) %>% 
      mutate(n_23 = NA, issue = "added") %>% 
      arrange(desc(n_24)) %>% 
    add_row(data1$observation_source_values %>%
      anti_join(data2$observation_source_values, by = "observation_source_value") %>% 
      select(observation_source_value, source_concept_name, obs_concept_id, n_23 =n) %>% 
      mutate(n_24 = NA, issue = "removed") %>% 
      arrange(desc(n_23)) 
    ) %>% 
    add_row(
      data1$observation_source_values %>%
        select(observation_source_value, source_concept_name, obs_concept_id, n_23 =n) %>% 
        inner_join(
          data2$observation_source_values %>% 
            select(observation_source_value, n_24 = n),
          by = "observation_source_value"
        ) %>% 
        filter(n_24 < n_23) %>% 
        mutate(issue = "decreased n") %>% 
        arrange(desc(n_23))
      ) 
  
  data_obs_all %>% 
    filter(n_24 >= 10 | n_23 >= 10) %>% 
    datatable(
      filter = "top",
      options = list(
              scrollX = TRUE,     
              scrollY = "400px",
              # pageLength = 100, 
              # scrollY = "120vh",  
              paging = FALSE,    # sin paginación
              dom = 't'           
            ))%>%
    formatStyle(
      'issue',
      target = 'row',
      backgroundColor = styleEqual(
        c("removed", "added", "decreased n"), 
        c("lightpink",  "lightgreen", "#FFD580")
      )
    )
}
```


#### Nationality


```{r,  echo=FALSE}
if ("obs_nationality" %in% names(data1)) {
  data1$obs_nationality %>%
    rename(n_23 = n) %>% 
    select(-db) %>% 
    full_join(
      data2$obs_nationality %>% 
        rename(n_24 = n) %>% 
        select(-db),
      by = "nationality"
    ) %>% 
    arrange(desc(n_24)) %>%
    mutate(
      n_23 = ifelse(n_23 <5, "<5", as.character(n_23)),
      n_24 = ifelse(n_24 <5, "<5", as.character(n_24))              
    ) %>% 
    datatable(options = list(
              scrollX = TRUE,
              scrollY = "400px",
              pageLength = 10000,
              dom = 't'
            ))
}
```


### Drug exposure

#### Drug quantity and days supply
Check for each type of drug record, how is the quantity value and days supply recorded (if it's NA or VALUE (zero/non-zero)).

```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("drug_quantity" %in% names(data1)) {
  data1$drug_quantity %>% 
    add_row(data2$drug_quantity) %>% 
    group_by(db, concept_name) %>% 
    mutate(total_n = sum(n)) %>% 
    ggplot(aes(x = concept_name, y = n, fill = quantity_val)) +
    geom_bar(
      aes(group = db),
      stat="identity",
      position = position_dodge(width=0.6),
      width=0.5
    )+
    geom_text(
      aes(label = db, group=db),
      position = position_dodge(width=0.6),
      vjust = -0.1,
      size = 3
    )+
    # scale_fill_manual(values = c("non-zero value" = "purple", "zero value" = "#1b9e67", "NA" = "grey")) +
    # scale_color_manual(values = c("non-zero value" = "purple", "zero value" = "#1b9e67", "NA" = "grey"))+
    labs(subtitle = "Drug quantity")
}
```


```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("drug_days_supply" %in% names(data1)) {
  data1$drug_days_supply %>% 
    add_row(data2$drug_days_supply) %>% 
    group_by(concept_name, db) %>% 
    ggplot(aes(x = concept_name, y = n, fill = days_supply_val)) +
    geom_bar(
      aes(group = db),
      stat="identity",
      position = position_dodge(width=0.6),
      width=0.5
    )+
    geom_text(
      aes(label = db, group=db),
      position = position_dodge(width=0.6),
      vjust = -0.1,
      size = 3
    )+
    # scale_fill_manual(values = c("non-zero value" = "purple", "zero value" = "#1b9e67", "NA" = "grey")) +
    # scale_color_manual(values = c("non-zero value" = "purple", "zero value" = "#1b9e67", "NA" = "grey"))+
    labs(subtitle = "Drug days supply")
}

```


#### Drug source values

Check how many drug concepts are mapped to drug_concept_id = 0

```{r, fig.width=8, fig.height=5, echo=FALSE}
if ("drug_source_values" %in% names(data1)) {
  data1$drug_source_values %>% 
    add_row(data2$drug_source_values) %>% 
    mutate(label = paste0(n_id0, " (", round(100 * n_id0 / n, 1), "%)")) %>%
    pivot_longer(
      cols = c(n, n_id0),
      names_to = "variable",
      values_to = "n"
    ) %>% 
    mutate(label = ifelse(variable == "n_id0", label , n)) %>% 
    ggplot(aes(x = variable, y = n, colour= db,  fill = db)) +
    geom_bar(stat="identity",position = position_dodge(width=0.6),width=0.6)+
    geom_text(
      aes(label = label, group=db),
      position = position_dodge(width=0.6),
      vjust = -0.3,
      size = 3
    ) +
    labs(subtitle = "Number of distinct drug source values (n_id0: those with drug_concept_id == 0)")+
    theme_minimal() 
}
```

Check how many records represents the drugs with drug_concept_id = 0

```{r, fig.width=8, fig.height=8, echo=FALSE}
if ("drug_source_values_id0_n" %in% names(data1) & "drugs_id_n" %in% names(data1)) {
  drugs_id_zero <- data1$drug_source_values_id0_n %>%
    group_by(drug_type_concept_id) %>% 
    summarise(n_rec = sum(n)) %>% 
    mutate(db = database1, drug_id = "id=0") %>% 
    add_row(
      data2$drug_source_values_id0_n %>%
        group_by(drug_type_concept_id) %>%
        summarise(n_rec = sum(n)) %>%
        mutate(db = database2, drug_id = "id=0")
      )
  
  drugs_id_nonzero <- data1$drugs_id_n %>% 
    add_row(data2$drugs_id_n) %>% 
    mutate(drug_id = "id") 
  
  n_tot <- drugs_id_zero %>% 
    add_row(drugs_id_nonzero) %>% 
    group_by(db) %>% 
    summarise(n_tot = sum(n_rec)) 
  
  drugs_id_zero %>% 
    add_row(drugs_id_nonzero) %>% 
    group_by(db, drug_id) %>% 
    summarise(n = sum(n_rec), .groups = "keep") %>% 
    left_join(n_tot, by="db") %>% 
    rename(drug_concept_id = drug_id) %>% 
    mutate(label = paste0(n, " (", round(100 * n / n_tot, 1), "%)")) %>%
    ggplot(aes(x = drug_concept_id , y = n, colour= db,  fill = db)) +
    geom_bar(stat="identity",position = position_dodge(width=0.6),width=0.6)+
    geom_text(
      aes(label = label, group=db),
      position = position_dodge(width=0.6),
      vjust = -0.3,
      size = 3
    ) +
    labs(subtitle = "Non-zero and zero drug_concept_id: number of records")+
    theme_minimal() 
}
```



### Conditions & medications

```{r,  echo=FALSE}
swr = function(string, nwrap=20) {
  paste(strwrap(string, width=nwrap), collapse="\n")
}
swr = Vectorize(swr)
```


```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("conditions_medications" %in% names(data1)) {
  data1$conditions_medications%>%
    add_row(data2$conditions_medications)%>%
    filter(grepl('ATC', cohort_name,ignore.case=TRUE))%>%
    mutate(cohort_name=swr(cohort_name))%>%
    ggplot(aes(x=cohort_start_date, y=n, color= db, fill=db))+
    facet_grid(cohort_name~ ., scales="free_y")+
    geom_bar(stat="identity", position="dodge")+
    theme(strip.text = element_text(size = 8),
          legend.position = "bottom") +
    labs(subtitle = "Cohorts of individuals with antidepressants, anxiolytics and hypnotics/sedatives (ATC 3rd level)")
}
```

```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("conditions_medications" %in% names(data1)) {
  data1$conditions_medications%>%
    add_row(data2$conditions_medications)%>%
    filter((grepl('Pregnancy',cohort_name)) |
   (grepl('perinatal',cohort_name)))%>%
    mutate(cohort_name=swr(cohort_name))%>%
    ggplot(aes(x=cohort_start_date, y=n, color= db, fill=db))+
    facet_grid(cohort_name~ ., scales="free_y")+
    geom_bar(stat="identity", position="dodge")+
    theme(strip.text = element_text(size = 8),
          legend.position = "bottom") +
    labs(subtitle = "Cohorts of individuals with certain conditions originating in the perinatal period")
}
```

```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("conditions_medications" %in% names(data1)) {
  data1$conditions_medications%>%
    add_row(data2$conditions_medications)%>%
    filter((grepl('heart',cohort_name)) |
          (grepl('veins',cohort_name)) |
          (grepl('arteries',cohort_name)))%>%
    mutate(cohort_name=swr(cohort_name))%>%
    ggplot(aes(x=cohort_start_date, y=n, color= db, fill=db))+
    facet_grid(cohort_name~ ., scales="free_y")+
    geom_bar(stat="identity", position="dodge")+
    theme(strip.text = element_text(size = 6),
          legend.position = "bottom") +
    labs(subtitle = "Cohorts of individuals with cardiovascular diseases")
}
```

```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("conditions_medications" %in% names(data1)) {
  data1$conditions_medications%>%
    add_row(data2$conditions_medications)%>%
    filter((grepl('nervous',cohort_name)) |
          (grepl('renal',cohort_name)))%>%
    mutate(cohort_name=swr(cohort_name))%>%
    ggplot(aes(x=cohort_start_date, y=n, color= db, fill=db))+
    facet_grid(cohort_name~ ., scales="free_y")+
    geom_bar(stat="identity", position="dodge")+
    theme(strip.text = element_text(size = 8),
          legend.position = "bottom") +
    labs(subtitle = "Cohorts of individuals with nervous and renal diseases")
}
```

### Sex-specific diseases
```{r,  fig.width=8, fig.height=6, echo=FALSE}
if ("cancer_sex" %in% names(data1)) {
  data1$cancer_sex%>%
    add_row(data2$cancer_sex)%>%
    ggplot(aes(x=cohort_name, y=n, color= db, fill=db))+
    facet_grid(sex ~ ., scales="free_y")+
    geom_bar(aes(group=db),stat="identity", position=position_dodge(width = 0.6),width = 0.6)+
    geom_text(aes(label = n, group = db), position=position_dodge(width = 0.6), vjust = -0.1, size = 3)+
    labs(subtitle = "Cohorts of individuals with certain sex-specific cancers")
}
```


### Concepts mapping

#### Source to concept map

Rows that have changed from previous instance to new one:

```{r,  fig.width=8, fig.height=5, echo=FALSE}
if ("source_to_concept" %in% names(data1)) {
  data1$source_to_concept %>% 
    select(
      source_code, 
      source_description = source_code_description, 
      target_voc_24= target_vocabulary_id, 
      target_id_24 = target_concept_id
    ) %>% 
    full_join(
      data2$source_to_concept %>% 
        select(
          source_code,
          target_voc_23= target_vocabulary_id,
          target_id_23 = target_concept_id
        ), 
      by ="source_code"
    ) %>% 
    filter(target_id_24 != target_id_23) %>% 
    select(source_code, source_description, target_id_23, target_voc_23, target_id_24, target_voc_24) %>% 
    mutate(issue = 
       ifelse(target_voc_23 =="None" & target_voc_24 !="None", "added", 
              ifelse(target_voc_23 !="None" & target_voc_24 =="None", "removed","changed")
              )
    ) %>% 
    mutate(issue = factor(issue, levels = c("changed", "added", "removed"))) %>% 
    arrange(issue) %>% 
    datatable(
      filter= "top",
      options = list(
        scrollX = TRUE,     
        scrollY = "400px",  
        # pageLength = 100,   
        paging=FALSE,
        dom = 't'           
      )) %>% 
      formatStyle(
        'issue',
        target = 'row',
        backgroundColor = styleEqual(
              c("changed", "added", "removed"), 
              c("#FFD580","lightgreen","lightpink")
        )
      )
}
```






